Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps

### 2014-04-08 ms.tex
starting reworking section on three parameter fits

It turns out that, for each of the \PLANCK~bands in which CO emission is
non-negligible (100, 217 and 353 GHz), only a single $N$ contributes ($N$=1, 
$N$=2 and $N$=3, respectively).

@@

\subsection{Sampling Parameters}
As discussed in $\S$\ref{sec:modeling}, our full-resolution fits
consider the ``global'' parameters $f_1$, $q_1/q_2$, $\beta_1$, $\beta_2$ to be
 fixed, while the dust spectrum normalization and dust temperature vary for
each line-of-sight. In order to predict the dust SED for a given pixel, we are 
therefore left with two remaining degrees of freedom, and must choose an 
appropriate set of two parameters to sample and thereby constrain via MCMC. To 
determine the SED normalization in each pixel, we draw samples in 
$\tilde{I}_{545}$, the broadband intensity in the 545 GHz bandpass, as defined 
in Equation \ref{eqn:inten}. With the four aforementioned global parameters 
fixed, the dust spectrum shape is determined entirely by the two dust 
temperatures, which are coupled. To constrain the dust temperatures,
 we sample in $T_2$, the hot dust temperature. For each sample in $T_2$, we 
compute the corresponding value of $T_1$, thereby specifying ($\beta$, $T$) for
both MBB components and thus fully specifying the SED shape.

@@

As mentioned previously, our baseline fits fix several parameters which
in principle could vary spatially. If we are willing to sacrifice angular
resolution in order to incorporate lower-frequency \PLANCK~bands and
enhance signal to noise, we can introduce additional free parameters
and run the Markov chains in higher dimensions.

We ran the Markov chains in three dimensions by allowing 
$f_1$ to be a third free parameter. We added to our standard posterior a 
term involving.

>>>>

It happens that, for each of the \PLANCK~bands in which CO emission is
non-negligible (100, 217 and 353 GHz), only a single $N$ contributes ($N$=1, 
$N$=2 and $N$=3, respectively).

@@

\subsection{Sampling Parameters}
\label{sec:samp}
As discussed in $\S$\ref{sec:modeling}, our full-resolution fits
consider the ``global'' parameters $f_1$, $q_1/q_2$, $\beta_1$, $\beta_2$ to be
 fixed, while the dust spectrum normalization and dust temperature vary for
each line-of-sight. In order to predict the dust SED for a given pixel, we are 
therefore left with two remaining degrees of freedom, and must choose an 
appropriate set of two parameters to sample and thereby constrain via MCMC. To 
determine the SED normalization in each pixel, we draw samples in 
$\tilde{I}_{545}$, the broadband intensity in the 545 GHz bandpass, as defined 
in Equation \ref{eqn:inten}. With the four aforementioned global parameters 
fixed, the dust spectrum shape is determined entirely by the two dust 
temperatures, which are coupled. To constrain the dust temperatures,
 we sample in $T_2$, the hot dust temperature. For each sample in $T_2$, we 
compute the corresponding value of $T_1$, thereby specifying ($\beta$, $T$) for
both MBB components and thus fully specifying the SED shape.

@@

As explained in $\S$\ref{sec:modeling} and $\S$\ref{sec:samp}, our 
full-resolution fits fix the parameters $f_1$, $q_1/q_2$, $\beta_1$, $\beta_2$ 
globally so that only the dust temperatures and SED normalization vary on a 
per-pixel basis. The reason for fixing so many parameters is that, at $6.1'$
FWHM, only five SED measurements are available per pixel.

% need some sort of add on to last sentence or another sentence entirely
% to the effect of ``staying in overconstrained regime''

However, sacrificing angular resolution in order to incorporate 
the \PLANCK~100, 143 GHz bands can allow us to introduce an additional free 
parameter and run our Markov chains in three-dimensional parameter space.

We ran the Markov chains in three dimensions by allowing 
$f_1$ to be a third free parameter. In these chains, we sampled the posterior
given by:

\begin{equation}
\label{eqn:post}
P(\tilde{I}_{545}, T_2, f_1|\{I\}) \propto \mathcal{L}(\{I\}|\tilde{I}_{545}, T_2, f_1)P(T_2)P(f_1)
\end{equation}
